Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-04-01 src-latex/parts/20-related-work.tex
Relecture globale et correction de coquilles

Several recent studies have focused on the impact of OCR quality on NER results. Most of the time, they have evaluated NER approaches based on deep learning architectures as they seem to adapt more easily to OCR errors than rule-based or more classical supervised approaches.
\cite{van2020assessing} use the English model \textit{en-core-web-lg} provided by the SpaCy \cite{spacy} library to perform NER on a corpus made of many journal articles with different levels of OCR errors.
For each OCRed article, a ground truth text is available so that the Word Error Rate (WER) can be computed.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F1-score for each NER class and each article, i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four supervised NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on CoNLL-02 and CoNLL-03 NER benchmark corpora, degraded by applying four different types of OCR noise. Overall, NER F-measure drops from 90\% to 50\% when the Word Error Rate increases from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors. 
Two approaches have been proposed by \cite{huynh2020use} and \cite{marz2021data}  to reduce the negative impact of OCR errors on NER performance on historical texts.
The former applies a spelling correction tool to several corpora with variable OCR error rates. 
As long as OCR errors remain low ($CER<2\%$ and $WER<10\%$), this strategy makes it possible to maintain good NER results. However, the F1-score starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalisation of an off-the-shelf NER model from modern texts to historical texts.
Finally, reusing a model trained on clean modern data, including embeddings computed on a historical corpus, and fine-tuned on a noisy historical ground truth has proven to be the most effective strategy.

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, \peroocr, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
In \cref{sec:dataset}, we will explain the evaluation protocol used to assess the combined performance of these OCR and NER systems.

\textbf{Tesseract} is a long-living project, born as a closed-sourced OCR at Hewlett-Packard in the eighties, it was progressively modernized, then open-sourced in 2005. From 2006 until November 2018, it was developed by Google and is still very active. We used in our tests version 4.1.1, released Dec. 26, 2019. Version 5, released on Nov. 30, 2021, has not been integrated in our tests yet.

@@

\textbf{CamemBERT} is well-known adaptation of the BERT transformer-based model for the French language~\cite{vaswani2017attention,devlin2018bert,martin-etal-2020-camembert}. Such language models have become a new paradigm for NER~\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer, usually referred as a ``head''. 
They can also be pre-trained in an unsupervised way on large amount of unlabelled texts for domain adaptation.

>>>>

Several recent studies have focused on the impact of OCR quality on NER results. Most of the time, they have evaluated NER approaches based on deep learning architectures as they seem to adapt more easily to OCR errors than rule-based or more classical supervised approaches.
\cite{van2020assessing} used the English model \textit{en-core-web-lg} provided by the SpaCy \cite{spacy} library to perform NER on a corpus made of many journal articles with different levels of OCR errors.
For each OCRed article, a ground truth text is available so that the Word Error Rate (WER) can be computed.
The performance of the NER model with respect to OCR quality is eventually assessed by computing the F1-score for each NER class and each article, i.e., each WER value.
\cite{hamdi2020assessing} performed a similar but more extensive evaluation on four supervised NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF.
They tested them on CoNLL-02 and CoNLL-03 NER benchmark corpora, degraded by applying four different types of OCR noise. Overall, NER F-measure drops from 90\% to 50\% when the Word Error Rate increases from 8\% to 50\%. However, models based on deep neural networks seem less sensitive to OCR errors. 
Two approaches have been proposed by \cite{huynh2020use} and \cite{marz2021data}  to reduce the negative impact of OCR errors on NER performance on historical texts.
The former applies a spelling correction tool to several corpora with variable OCR error rates. 
As long as OCR errors remain low ($CER<2\%$ and $WER<10\%$), this strategy makes it possible to maintain good NER results. However, the F1-score starts to decrease significantly when OCR errors exceed these thresholds.
The latter work focuses on adapting the training data to facilitate the generalisation of an off-the-shelf NER model from modern texts to historical texts.
Finally, reusing a model trained on clean modern data, including embeddings computed on a historical corpus, and fine-tuned on a noisy historical ground truth has proven to be the most effective strategy.

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, \peroocr, and Kraken. We also adopted two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that can be adapted to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
In \cref{sec:dataset}, we will explain the evaluation protocol used to assess the combined performance of these OCR and NER systems.

\textbf{Tesseract} is a long-living project, born as a closed-sourced OCR at Hewlett-Packard in the eighties; it was progressively modernized, then open-sourced in 2005. From 2006 until November 2018, it was developed by Google and is still very active. We used in our tests the version 4.1.1, released Dec. 26, 2019. Version 5, released on Nov. 30, 2021, has not been integrated in our tests yet.

@@

\textbf{CamemBERT} is well-known adaptation of the BERT Transformer-based model for the French language~\cite{vaswani2017attention,devlin2018bert,martin-etal-2020-camembert}. Such language models have become a new paradigm for NER~\cite{li2020}. 
The learned contextual embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer, usually referred to as a ``head''. 
They can also be pre-trained in an unsupervised way on large amount of unlabelled texts for domain adaptation.
